Apache Storm

### 2017-11-28 paper.tex
Minor Introduction done

\usepackage[capitalise,nameinlink,ngerman]{cleveref}
%\usepackage[capitalise,nameinlink,english]{cleveref}
%Nice formats for \cref - only for English texts
%\crefname{section}{Sect.}{Sect.}
%\Crefname{section}{Section}{Sections}

@@

\title{Paper Title}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

\author{Vorname Nachname}

\supervisor{Vorname Nachname}

@@

\semester{WS 2015/2016}

\abgabedatum{Stuttgart, 22.06.2015}

\institute{\email{autor.eins@beispiel.de}}

\frontpagede % creates the frontpage (in German)
%\frontpageen % creates the frontpage (in English)

@@

\begin{abstract}
Die Kurzfassung sollte den Inhalt der Arbeit kurz wiedergeben und aus mindestens 70 und maximal 150 Wörtern bestehen.
Sie wird in einer 9-Punkt Schrift gesetzt und 1 cm eingerückt von rechts und links.
Vor und nach der Kurzfassung sind zwei leere Zeilen.
\end{abstract}

%\begin{keywords}
%keyword1, keyword2
%\end{keywords}

>>>>

%\usepackage[capitalise,nameinlink,ngerman]{cleveref}
\usepackage[capitalise,nameinlink,english]{cleveref}
%Nice formats for \cref - only for English texts
%\crefname{section}{Sect.}{Sect.}
%\Crefname{section}{Section}{Sections}

@@

\title{Apache Storm}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

\author{Aanal Raj Basaula}

\supervisor{Matthias Wieland}

@@

\semester{WS 2017/2018}

\abgabedatum{Stuttgart, 11.12.2017}

\institute{\email{aanal.basaula@gmail.com}}

%\frontpagede % creates the frontpage (in German)
\frontpageen % creates the frontpage (in English)

@@

\begin{abstract}
In today's world everyone is connected to this ever increasing network of computers be it via a Personal computer, a smart phone or an Embedded Device such as your smart home appliances. These devices generate a huge amounts of data every instance, that can be analyzed to leverage business opportunities previously undiscovered. To be able to discern these windows of opportunities, one must be able to process and analyze the data. In this report we talk about such scenario and the available tools which allows us to process large data streams with minimum latency.
\end{abstract}

\begin{keywords}
Apache Storm, Stream Processing, Real Time Processing, Big Data
\end{keywords}

\section{Introduction}

\textbf{Data} today is generated by a lot of devices that are connected to the internet and the amount of data being generated at any instance is increasing rapidly. The above mentioned device could be a Personal Computer, a Smart phone, or even an Embedded System. Due to the rapid adoption of Internet of Things, data is being generated at a rate that is unprecedented. The sheer volume of data generated and at the rate at which it is being generated can be termed as Big Data. \textbf{Big Data} made it's appearance in 1998 SGI slide by John Mashey and now is of interest to a lot of financial as well as research institutions.[1]

Data can be considered the oil of the current age, because with huge amounts of data one can determine hidden patterns. A lot of companies utilize pattern recognition on big data to open opportunities for revenue generation whereas research institutions use it to discover something new. The question on how to classify any data as big data can be answered by using the 3Vs of big data: Volume, Variety and Velocity. Any data with big volume or variety (such as text, video, images, etc) or that gets generated rapidly can be considered as big data. In this paper regarding \textbf{Apache Storm} we consider the third V of big data to be the influencing factor.

\textbf{Data Stream} is a sequence of data flowing from a source to a destination, for example a sensor reporting the temperature to a server. The sensor measures the temperature periodically and updates it to the server. Another example could also be the purchase requests of your product. In all of these scenarios, the data is continuously being generated. Traditionally analyzing of these types of data requires storage of these data onto persistence and later batch processing it to discern patterns as well as other useful information. But, with the help of \textbf{Apache Storm} we are able to process these data as they are generated with minimum amount of latency.

This benefit could be a major game changer for many companies as Stream processing of data allows Real Time Analysis. As an example, an online store could monitor its purchase requests for best performing and least performing articles and could offer discounts on the articles not performing good to increase their sales volume. This small change could increase the earnings of a company and will surely be advantageous.

\section{Apache Storm: Concepts}
